Security vs. Maintainability: \\ Fixing Vulnerabilities Obfuscates your Code

### 2019-01-28 paper/ICPC19/icpc19.tex
sfrac
more results

The impact of security and baseline commits in the maintainability of open-source software is presented in Figure \ref{fig:secvsreg}. For each type of change, three types of impact of refactorings in the software maintainability are presented: \emph{negative}, i.e., maintainability decreased (\emph{red}); \emph{none}, i.e., the maintainability did not suffer any changes (\emph{yellow}); and, \emph{positive}, i.e., the maintainability increased (\emph{negative}).

@@

>>>>

The impact of security and baseline commits in the maintainability of open-source software is presented in Figure \ref{fig:secvsreg}. For each type of change, three types of impact of refactorings in the software maintainability are presented: \emph{negative}, maintainability decreases (\emph{red}); \emph{none}, maintainability stays the same (\emph{yellow}); and, \emph{positive}, maintainability increases (\emph{green}). In front of each group, it is presented the mean ($\overline{x}$) and median ({$\widetilde{x}$) of the maintainability difference and the p-value resulting from the Wilcoxon signed-rank test.

@@

Regarding security commits results, we observe that maintainability decreases in 40.20\% (244), increases in 29.33\% (178) and stays the same in 30.5\% (185) of the cases after security refactorings being applyed. The resulting p-value of the Wilcoxon signed-rank test is $1.21$x$10^{-10}$. Since the p-value is below the significance level of $0.05$, it is fair to state that \emph{security refactorings have a negative impact in the maintainability of open-source software}.

For regular commits, we also observe that maintainability decreases in 41.35\% (251) of the cases after regular refactorings being applyed. But in contrast to security commits, it increases in 58.16\% (353) and stays the same in 0.5\% (3). The resulting p-value of the Wilcoxon signed-rank test is $1.54$x$10^{-6}$. Since the p-value is below the significance level of $0.05$, it is fair to state that \emph{regular refactorings have a positive impact in the maintainability of open-source software}.
